\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{makecell}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[normalem]{ulem}

\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

\usepackage[
backend=biber,
style=numeric,
sorting=none,
citestyle=ieee
]{biblatex}

\addbibresource{references.bib}

%opening
\title{Software Requirement Specification Document for SWE230 Course Project}
\author{
Supervised by: Dr. Essam Eliwa, Eng. Nada Ayamn
}

\begin{document}
\maketitle

\begin{table}[htp]
\caption{Document version history}
\begin{center}
\begin{tabular}{|c|c|l|}
\hline
\thead{Version}    & \thead{Date} & \thead{Reason for Change}  \\ \hline
1.0 & 18-Feb-2023   & \makecell[l]{SRS First version’s specifications are defined.}   \\ \hline
%1.1 & 2-Dec-2022   & \makecell[l]{....\\.....\\........} \\ \hline
%1.3 & 10-Dec-2022   & \makecell[l]{......\\......} \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[htp]
\begin{tabular}{cc}
\thead{Project:}    & {........................................................}   
\end{tabular}
\end{table}

\pagebreak
\tableofcontents
\pagebreak
\begin{abstract}
Project abstract (Word Limit 150)
\end{abstract}


\section{Introduction}
\subsection{Purpose of this document}
The purpose of this document is to provide an overview of the ..... project, including a detailed description of the project's functional and non-functional requirements, as well as the design and constraints that this system shall meet. This document targets the project's internal (developers, supervisors) and external (end-users) stakeholders. This document is restricted to the MIU Computer Science school premises. The project is implemented under the guidance of SWE230 course professors. 

\subsection{Scope of this document}
This SRS document
\begin{itemize}
    \item Specifies the required functions to be implemented for the SWE230 web application project. 
    \item Gives guidelines for applying the functional and non-functional requirements and related processes.
    \item Specifies the final deliverables of the project.
    \item Specifies the involved stakeholders. 
    \item Specifies a guideline for the project schedule.
\end{itemize}


%\subsection{Business Context}
%200 word Limit


\section{Similar Systems}
\subsection{Academic}
% Two related paper with references

\subsection{Business Applications}
%Include a maximum of Two similar business applications with references.  (if applicable).
\section{System Description}

\subsection{Problem Statement}
200 word Limit

\subsection{System Overview}

\subsection{System Scope}

\subsection{System Context}

\subsection{Objectives}

\subsection{ User Characteristics}
100 word Limit.


\pagebreak 
\section{Functional Requirements}
\subsection{System Functions}\label{System Functions}

\section{Design Constraints}
100 word Limit.

\subsection{ Standards Compliance}

\subsection{ Hardware Limitations}


\section{Non-functional Requirements}
200 word Limit.

% \section{Data Design}
% Data Description (200 word Limit)


% \section{Preliminary Object-Oriented Domain Analysis}
% Initial Class Diagram


\section{Operational Scenarios}

\section{Project Plan}


\section{Appendices}

\subsection{Definitions, Acronyms, Abbreviations}


\printbibliography
Note that you should use a minimum of ten references (80\% Academic)
\end{document}

